\section{Bibliografia}

\begin{enumerate}

\item {\textit {Courtemanche, Meredith; Mell, Emily; Gills, Alexander S. "What Is DevOps? The Ultimate Guide". TechTarget. [Dostęp: 2023-01-22]}}
\item {\textit {Ray, Partha Pratim. “An Introduction to Dew Computing: Definition, Concept and Implications.” IEEE Access 6 (2018): 723-737.}}

\item {\textit {"Better Language Models and Their Implications". OpenAI. 2019-02-14. Archived from the original on 2020-12-19.[Dostęp: 2019-08-25]}}
\item {\textit {Russell, Stuart J.; Norvig, Peter. (2021). Artificial Intelligence: A Modern Approach (4th ed.). Hoboken: Pearson. ISBN 978-0134610993. LCCN 20190474}}
\item {\textit {Reddy, Martin (2011). API Design for C++. Elsevier Science. p. 1. ISBN 9780123850041. [Dostęp: 2023-03-21]}}
\item {\textit {Don, Norman; Jakob, Nielsen. "The Definition of User Experience (UX)". Nielsen Norman Group. [Dostęp: 2 March 2021.]}}
\item {\textit {HTML: HyperText Markup Language | MDN \\ https://developer.mozilla.org/en-US/docs/Web/HTML}}
\item {\textit {"CSS developer guide". MDN Web Docs. \\ https://developer.mozilla.org/en-US/docs/Learn/CSS}}
\item {\textit {Sztuczna inteligencja w pracy informatyka. Marcin Szeliga \\ https://itprofessional.pl/2024/04/05/sztuczna-\\inteligencja-w-pracy-informatyka/}}
\item {\textit {Yuchen Jiang, Xiang Li, Hao Luo, Shen Yin, Okyay Kaynak. "Quo vadis artificial intelligence?". https://link.springer.com/article/10.1007\\/s44163-022-00022-8. 2022-03-07}}
\item {\textit {What is ChatGPT?. https://help.openai.com/en/\\articles/6783457-what-is-chatgpt}}
\item {\textit {Michael Sailer, Lisa Homner, "The Gamification of Learning: a Meta-analysis" https://link.springer.com/article/10.1007/s10648-019-09498-w. 2019-08-15}}
\item {\textit {Introducing LLaMA: A foundational, 65-billion-parameter large language model. https://ai.meta.com/blog/large-language-model-llama-meta-ai/}}
\item {\textit {Stable LM Zephyr 3B: A Powerful and Efficient Language Model for Edge Devices. Mirza Causevic. \\ https://medium.com/@mizcausevic/stable-lm-zephyr-3b-a-\\powerful-and-efficient-language-model-for-edge-devices-14bb2de04c91}}
\item {\textit {Jules White, Quchen Fu, Sam Hays, Michael Sandborn, Carlos Olea, Henry Gilbert, Ashraf Elnashar, Jesse Spencer-Smith, Douglas C. Schmidt, "A Prompt Pattern Catalog to Enhance Prompt Engineering with ChatGPT" Cornell University https://arxiv.org/abs/2302.11382, 2023-02-21}}
\item {\textit {ArtPrompt: ASCII Art-based Jailbreak Attacks against Aligned LLMs.Jiang, Fengqing and Xu, Zhangchen and Niu, Luyao and Xiang, Zhen and Ramasubramanian, Bhaskar and Li, Bo and Poovendran, Radha. \\ https://arxiv.org/pdf/2402.11753 }}
\item {\textit {Baseline Defenses for Adversarial Attacks Against Aligned Language Models. Jain, Neel and Schwarzschild, Avi and Wen, Yuxin and Somepalli, Gowthami and Kirchenbauer, John and Chiang, Ping-yeh and Goldblum, Micah and Saha, Aniruddha and Geiping, Jonas and Goldstein, Tom. https://arxiv.org/pdf/2309.00614}}
\item {\textit {Quinn, Joanne (2020). Dive into deep learning: tools for engagement. Thousand Oaks, California. p. 551. ISBN 978-1-5443-6137-6}}
\item {\textit {Why ChatGPT and Bing Chat are so good at making things up. Benj Edwards. https://arstechnica.com/information-technology/\\2023/04/why-ai-chatbots-are-the-ultimate-bs-machines-and-how\\-people-hope-to-fix-them/}}
\item {\textit {The 15 Biggest Risks Of Artificial Intelligence. Bernard Marr. \\ https://www.forbes.com/sites/bernardmarr/2023/06/02/the-15-biggest-risks\\-of-artificial-intelligence/}}
\item {\textit {P. P. Ray, "An Introduction to Dew Computing: Definition, Concept and Implications," in IEEE Access, vol. 6, pp. 723-737, 2018, doi: 10.1109/ACCESS.2017.2775042}}
\item {\textit{Sunyaev, A. (2020). Cloud Computing. In: Internet Computing. Springer, Cham. \url{https://doi.org/10.1007/978-3-030-34957-8_7}}}
\item {\textit {Mikrousługi na platformie Azure.  https://azure.microsoft.com/pl-pl/solutions/\\microservice-applications}}
\item {\textit {Fowler, Martin (2002). Patterns of Enterprise Application Architecture. Addison-Wesley Professional. ISBN 978-0321127426}}
\item {\textit {Salecha, R. (2022). What Is GitOps?. In Practical GitOps: Infrastructure Management Using Terraform, AWS, and GitHub Actions (pp. 1-30). Berkeley, CA: Apress.}}
\item {\textit {DeJonghe, Derek. Nginx CookBook. O'Reilly Media, 2020.}}
\item {\textit {Fundamentals of Software Architecture: An Engineering Approach (version First edition). 2020 First ed. Sebastopol, CA: O’Reilly Media. }}
\item {\textit {Mochammad Fariz Syah Lazuardy
, Dyah Anggraini. “Modern Front End Web Architectures with React.Js
and Next.Js" International Research Journal of Advanced Engineering and Science, https://irjaes.com/\\wp-content/uploads/2022/02/IRJAES-V7N1P162Y22.pdf}}
\item {\textit {Alex Banks, Eve Porcello. "Learning React: Modern Patterns for Developing React Apps". O'Reilly 2020-06-12}}
\item {\textit {Mikrousługi .NET: architektura konteneryzowanych aplikacji .NET. \\ https://learn.microsoft.com/pl-pl/dotnet/architecture/microservices/}}
\item {\textit{Roger Villela. "Exploring the .NET Core 3.0 Runtime". Apress 2019-09-06}}
\item {\textit {John, Bradley; Nat, Sakimura; Michael, Jones. "JSON Web Token (JWT)". https://datatracker.ietf.org/doc/html/rfc7519, 2015-05}}
\item {\textit {Saineshwar Bageri. "RabbitMQ With C\#". BPB PUBN 2018-11-08}}

\end{enumerate}